### 2020-02-03 First_Shortening_version/Manuscript_short.Rmd
cleanup of previous submission materials and versions, organized to move forward with PlosBio/PNAS version

  Most animal predators use specific structures to capture and subdue prey. Raptors have claws and beaks, snakes have fangs, wasps have stingers, and cnidarians have nematocyst-laden tentacles. The functional morphology of these structures is critical to their ability to successfully capture prey [@schmitz2017predator]. Long-term adaptive evolution in response to the defense mechanisms of the prey (*e.g.*, avoidance, escape, protective barriers) leads to modifications that can counter those defenses. The more specialized the diet of a predator is, the more specialized its structures need to be to efficiently overcome the challenges posed by the prey. Understanding the relationships between predatory and morphological specializations is necessary to contextualize the phenotypic diversity of predators, quantify the importance of ecological diversification in generating this diversity, and to understand the organismal determinants of food web structure. However, for many clades of predators, there is scarce knowledge on how these specializations evolved with each other. The primary questions we set out to answer are: how do predator specialists and generalists evolve, and how does predatory specialization shape morphological evolution?

  Siphonophores (Cnidaria: Hydrozoa) are a clade of organisms bearing modular structures that are exclusively used for prey capture: the tentilla (Fig. \@ref(figure1)). The tentilla have great morphological variation across species [@mapstone2014global] (Fig. \@ref(figure2)), which makes them an ideal system to study the relationships between functional traits and prey specialization. Like a head of coral, a siphonophore is a colony bearing many feeding polyps (Fig. \@ref(figure1)). Each feeding polyp has a single tentacle, which bears a series of side branches known as tentilla. Like other cnidarians, siphonophores capture prey with nematocysts, harpoon-like stinging capsules borne within specialized cells known as cnidocytes. Unlike the prey capture apparatus of most other cnidarians, siphonophore tentacles carry their cnidocytes in extremely complex and organized batteries [@skaer1988formation] which are located in their tentilla. While nematocyst batteries and clusters in other cnidarians are simple static scaffolds for cnidocytes, siphonophore tentilla have their own reaction mechanism, triggered upon encounter with prey. When it fires, a tentillum undergoes an extremely fast conformational change that wraps it around the prey, maximizing the surface area of contact for nematocysts to fire on the prey [@Mackie:1987uy]. In addition, some species have elaborate fluorescent and bioluminescent lures on their tentilla to attract prey with aggressive mimicry [@purcell1980influence;@haddock2005bioluminescent;@haddock2015fluorescent].

  Siphonophores bear four major nematocyst types in their tentacles and tentilla (Fig. \@ref(figure1)F).. The largest type, heteronemes, have open-tip tubules characterized by bearing a distinctly wider spiny shaft at the proximal end of the everted tubule. These are typically found flanking the proximal end of the cnidoband. The most abundant type, haplonemes, have no distinct shaft, but similarly to heteronemes, their tubules have open tips and can be found in the cnidoband. Both heteronemes and haplonemes bear short spines along the tubule and can be toxic and penetrate the surface of some prey types. In the terminal filament, siphonophores bear two other types of nematocysts, characterized by their adhesive function, closed tip tubules, and lack of spines on the tubule. These are the desmonemes (a type of adhesive coiled-tubule spironeme), and rhopalonemes (a siphonophore-exclusive nematocyst type with wide tubules).

@@

  Our work builds upon previous pioneering studies that have explored the relationships between tentilla and diet, and showed that siphonophores are a robust system for the study of predatory specialization via morphological diversification. [@purcell1984functions] and [@purcell1988correlation] showed clear relationships between diet, tentillum, and nematocyst characters in co-occurring epipelagic siphonophores for a small subset of extant epipelagic siphonophore species.

>>>>

  Most animal predators use specific structures to capture and subdue prey. Raptors have claws and beaks, snakes have fangs, wasps have stingers, and cnidarians have nematocyst-laden tentacles. The functional morphology of these structures is critical to their ability to successfully capture prey [@schmitz2017predator]. Long-term adaptive evolution in response to the defense mechanisms of the prey (*e.g.*, avoidance, escape, protective barriers) leads to modifications that can counter those defenses. The more specialized the diet of a predator is, the more specialized its structures need to be to efficiently overcome the challenges posed by the prey. Understanding the relationships between morphology and predatory specialization is necessary to contextualize the phenotypic diversity of predators, quantify the importance of ecological diversification in generating this diversity, and to understand the organismal determinants of food web structure. However, for many clades of predators, there is scarce knowledge on how these specializations evolved with each other. The primary questions we set out to answer are: how do predator specialists and generalists evolve, and how does predatory specialization shape morphological evolution?

  Siphonophores (Cnidaria: Hydrozoa) are a clade of organisms bearing modular structures that are exclusively used for prey capture: the tentilla (Fig. \@ref(figure1)). The tentilla have great morphological variation across species [@mapstone2014global] (Fig. \@ref(figure2)), which together with their unconfounded function, makes them an ideal system to study the relationships between functional traits and prey specialization. Like a head of coral, a siphonophore is a colony bearing many feeding polyps (Fig. \@ref(figure1)). Each feeding polyp has a single tentacle, which bears a series of side branches known as tentilla. Like other cnidarians, siphonophores capture prey with nematocysts, harpoon-like stinging capsules borne within specialized cells known as cnidocytes. Unlike the prey capture apparatus of most other cnidarians, siphonophore tentacles carry their cnidocytes in extremely complex and organized batteries [@skaer1988formation] which are located in their tentilla. While nematocyst batteries and clusters in other cnidarians are simple static scaffolds for cnidocytes, siphonophore tentilla have their own reaction mechanism, triggered upon encounter with prey. When it fires, a tentillum undergoes an extremely fast conformational change that wraps it around the prey, maximizing the surface area of contact for nematocysts to fire on the prey [@Mackie:1987uy]. In addition, some species have elaborate fluorescent and bioluminescent lures on their tentilla to attract prey with aggressive mimicry [@purcell1980influence;@haddock2005bioluminescent;@haddock2015fluorescent].

  Siphonophores bear four major nematocyst types in their tentacles and tentilla (Fig. \@ref(figure1)F).. The largest type, heteronemes, have open-tip tubules characterized by bearing a distinctly wider spiny shaft at the proximal end of the everted tubule. These are typically found flanking the proximal end of the cnidoband. The most abundant type, haplonemes, have no distinct shaft, but similarly to heteronemes, their tubules have open tips and can be found in the cnidoband. Both heteronemes and haplonemes bear short spines along the tubule. Both can be toxic and penetrate the surface of some prey types. In the terminal filament, siphonophores bear two other types of nematocysts, characterized by their adhesive function, closed tip tubules, and lack of spines on the tubule. These are the desmonemes (a type of adhesive coiled-tubule spironeme), and rhopalonemes (a siphonophore-exclusive nematocyst type with wide tubules).

@@

  Our work builds upon previous pioneering studies that have explored the relationships between tentilla and diet, and showed that siphonophores are a robust system for the study of predatory specialization via morphological diversification. Purcell (1984) and Purcell (1988) showed clear relationships between diet, tentillum, and nematocyst characters in co-occurring epipelagic siphonophores for a small subset of extant epipelagic siphonophore species.
